Inference methods comparison for the simplified Naomi model

### 2023-02-10 src/naomi-simple_compare/comparison.Rmd
Add KS summary plot split by hyperparameters and latent, move to jitterplot rather than boxplot, save KS summary table

ggplot(ks_summary, aes(x = `KS(TMB, tmbstan)`, y = `KS(aghq, tmbstan)`)) +
  geom_point(alpha = 0.5) +
  xlim(0, 1) +
  ylim(0, 1) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
  labs(x = "KS(TMB, tmbstan)", y = "KS(aghq, tmbstan)") +
  theme_minimal()

ks_summary %>%
  mutate(`KS difference` = `KS(TMB, tmbstan)` - `KS(aghq, tmbstan)`) %>%
  ggplot(aes(x = `KS difference`)) +
    geom_boxplot(width = 0.5) +
    coord_flip() +
    labs(x = "KS(TMB, tmbstan) - KS(aghq, tmbstan)") +
    theme_minimal()
```

>>>>

r <- adam$quad$obj$env$random
x_names <- names(adam$quad$obj$env$par[r])
theta_names <- names(adam$quad$obj$env$par[-r])

dict <- data.frame(
  Parameter = c(x_names, theta_names),
  Type = c(rep("Latent field", length(x_names)), rep("Hyperparameters", length(theta_names)))
)

ks_summary <- ks_summary %>%
  left_join(dict, by = "Parameter")

summary_ks_plot <- function(ks_summary, method1, method2) {
  ks_method1 <- paste0("KS(", method1, ", tmbstan)")
  ks_method2 <- paste0("KS(", method2, ", tmbstan)")

  scatterplot <- ggplot(ks_summary, aes(x = .data[[ks_method1]], y = .data[[ks_method2]])) +
    geom_point(alpha = 0.2) +
    annotate(geom = "polygon", x = c(-Inf, Inf, Inf), y = c(-Inf, Inf, -Inf), fill = multi.utils::cbpalette()[3], alpha = 0.1) +
    annotate(geom = "polygon", x = c(-Inf, Inf, -Inf), y = c(-Inf, Inf, Inf), fill = multi.utils::cbpalette()[5], alpha = 0.1) +
    xlim(0, 1) +
    ylim(0, 1) +
    geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
    labs(x = ks_method1, y = ks_method2) +
    theme_minimal()

  ks_summary[["KS difference"]] <- ks_summary[[ks_method1]] - ks_summary[[ks_method2]]

  jitterplot <- ggplot(ks_summary, aes(x = Type, y = `KS difference`)) +
    geom_jitter(width = 0.1, alpha = 0.2) +
    labs(x = "", y = paste0(ks_method1, " - ", ks_method2)) +
    theme_minimal()

  scatterplot + jitterplot
}

summary_ks_plot(ks_summary, "TMB", "aghq")
summary_ks_plot(ks_summary, "TMB", "adam")
summary_ks_plot(ks_summary, "aghq", "adam")

(ks_summary_out <- ks_summary %>%
  group_by(Type) %>%
  summarise(
    TMB = mean(`KS(TMB, tmbstan)`),
    aghq = mean(`KS(aghq, tmbstan)`),
    adam = mean(`KS(adam, tmbstan)`)
  ))
```

Save some things for output:

```{r}
pdf("ks_summary_tmb_adam.pdf", h = 4, w = 6.25)
summary_ks_plot(ks_summary, "TMB", "adam")
dev.off()

saveRDS(ks_summary_out, "ks_summary_out.rds")
```
